A simulation model of DNA methylation data

### 2015-04-03 Rmarkdown/methsim.Rmd
Scattered thoughts on simulating DMRs

\subsection{Parameter estimation}

>>>>

An obvious application of `methsim` is to simulate data to be used in a study comparing methods for identifying differential methylation. This requires a particularly controllable method for inducing differences in `SimulatedMethylome` objects. The user wants to provide a set of methylation loci, either individual loci or as regions, and the expected difference in methylation levels at these regions.

__Scattered thoughts below__

1. Individual loci: Want to specify $B_{i} = \sum_{\tilde{h} = 1}^{n_{\tilde{h}}} W_{r_{i}, \tilde{h}} \times Z_{i, \tilde{h}}$, i.e., fix $\mathbf{W_{i, \cdot}}$ and $\mathbf{Z_{i, \cdot}}$.
2. Regionwise: Want to specify $mean(B_{r_{i}})$ (i.e., average $B$ across all loci in $r_{i}$). Could do this by applying (1) to all loci in the region or by specifying $B_{r_{i}}$ and hoping it just works out in the simulation.

Perhaps both could be achieved by holding $Z$ fixed and varying $W$? Is that like assuming that the heterogeneity is causing the DMRs (or will it be interpreted that way)? Would tweaking $W$ to guarantee a particular $B$ be a computationally feasible strategy? Or would it be easier to specify the desired $B$ and simulate the region (this wouldn't guarantee $B$ is the desired value but should equal it "on average")?
